---
title: "Lab 8"
author: "Sophia Leiker"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(broom)
library(here)
library(corrplot)
```

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

### Create a subset with 4 cities

Task: create a subset (called homes_subset) that only contains observations where the city is:

- "San Luis Obispo"
- "Atascadero"
- "Arroyo Grande"
- "Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo",
                     "Atascadero",
                     "Arroyo Grande",
                     "Santa Maria-Orcutt"))

#Do not use double equals because then it checks line by line 
```


### A little exploration

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

```{r, include=FALSE, eval=FALSE}
homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price),
            sd_price = sd(Price))

# eval=FALSE doesn't run the code
# include=FALSE means that the code runs but does not show up in the knitted markdown doc
```

Task: explore the relationship between square footage and home price (from homes_subset) in scatterplot

```{r}
ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm")
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home Price, using "homes_subset".

Create 2 different permutations of this model:

(1) Price ~ City, Bedrooms, Bathrooms, SqFt, Status (lm1)
(2) Price ~ City, SqFt, Status (lm2)
(3) Try another one (lm3)

```{r}
lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)
summary(lm1)

lm2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)

lm3 <- lm(Price ~ City + SqFt, data = homes_subset)

#If I wanted San Luis Obisbo to be the reference level:
# Use fct_relevel to specify a new reference level

#adjusted R squared value of 0.53 means that 53% of sale price is explained by variables in this model, the p-value the model significance overall 

new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo"))

lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)
summary(lm_slo)

```

### Explore correlations between quantitative variables

Task: make a subset called homes_quant (starting from homes_subset) that only contains the variables from Price through SqFt)

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_cor <- cor(homes_quant)

corrplot(homes_cor) #you can add method = "circle" or "ellipse" to change visualization
```

```{r}
summary(lm2)
```

### Compare AIC Values

```{r}
AIC(lm1)
AIC(lm2)

#lower AIC values indicate better model fit for variables included (note: looking at the tradeoff for complexity in terms of the number of variables that are included in relationship to the explanatory value of the model)
```

### Use modelsummary() to return multiple model outputs

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### Check out diagnostic plots for lm1

```{r}
plot(lm1)
```

### Use broom::augment() to return the predictions for exiting observations

```{r}
homes_predictions <- augment(lm1)
```

# Make a histogram of the residuals from this model (lm1)

```{r}
ggplot(data = homes_predictions, aes(x= .resid)) +
         geom_histogram()
```

# BRANCHES ARE AWESOME